Additional analyses

### 2023-10-27 procesamiento/prod_analysis-tables-macro.Rmd
modelos ordinales macro

---
title: "Cross-level interactions"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

```{r full-clmm-macro,results='asis'}

>>>>

---
title: "Additional analyses"
subtitle: "Cross-level interactions"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

@@

```{r full-clmm-macro,results='asis'}
htmltools::includeHTML("../output/fullsample-ologit-homclass-full-strong-weak-macro.html")
```

### 2023-10-27 procesamiento/prod_analysis-tables-micro.Rmd
modelos ordinales macro

---
title: "Additional analyses"
subtitle: "Full sample"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Additional analyses"
subtitle: "Micro level"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/custom.css" # custom CSS para html
output: 
  html_document: 
    toc: false
    code_folding: hide
    toc_float: 
      collapsed: true
      smooth_scroll: false
      number_sections: true
editor_options: 
  chunk_output_type: console
---
